---
title: "Alcohol vs Seat choice"
author: "Karla Cota Lopez"
date: "October 1,2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question 
Is there a difference between the alcohol consumed between the row you choose to sit in??

#Method
predict alcohol consumption based on where you sit.

$H_0$: There is no difference between the alcohol consumed between the row you choose to sit in

$H_A$: There is a difference between the alcohol consumed between the row you choose to sit in

alcohol is numerical
seat is categorical
Use file num~cat
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
This boxplot shows us that those who choose to sit in the back tend to drink more alcohol.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Boxplot shows those who drink more alcohol sit in the back.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The average of alcohol consumption for those in the back seats is 8.5 ounces.
The average of alcohol consumption for those in the front is 1.7 ounces.  
The average of alcohol consumption for those in the middle is 3.3 ounces.   

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116 which is lower than 0.05
Thus, we reject the null hypothesis 

```{r}
plot(TukeyHSD(model1))
```
The Tukey shows us that the middle-front has no difference
The middle-back does have a difference
The front-back does have a difference

## Conclusions
We conclude that those who sit in the back seats tend to drink more alcohol than those who choose to sit in the front and middle seats. The numerical results show us that those who sit in the back on average consume 8.5 ounces where those who sit in the front consume 1.7 and those in the middle consume 3.3 ounces. We found the p-value to be 0.000116 which is less than 0.05 which means we then reject the null hypothesis as there is a difference in alcohol consumed based on were you sit.

