---
title: "Alcohol vs Seat choice"
author: "Karla Cota Lopez"
date: "October 1,2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question 
Is there a difference between the alcohol consumed between the row you choose to sit in??

#Method
predict alcohol consumption based on where you sit.

$H_0$: There is no difference between the alcohol consumed between the row you choose to sit in

$H_A$: There is a difference between the alcohol consumed between the row you choose to sit in

alcohol is numerical
seat is categorical
Use file num~cat
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
This boxplot shows us that those who choose to sit in the back tend to drink more alcohol.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Boxplot shows those who drink more alcohol sit in the back.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The average in ounces of alcohol consumption for those in the back seats is 8.5.   
The average in ounces of alcohol consumption for those in the front is 1.7.  
The average in ounces of alcohol consumption for those in the middle is 3.3.  

## Inferential Tests

## Conclusions


