---
title: "Alcohol vs Seat choice"
author: "Karla Cota Lopez"
date: "October 1,2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question 
Is there a difference between the alcohol consumed between the row you choose to sit in??

#Method
predict alcohol consumption based on where you sit.

$H_0$: There is no difference between the alcohol consumed between the row you choose to sit in

$H_A$: There is a difference between the alcohol consumed between the row you choose to sit in

alcohol is numerical
seat is categorical
Use file num~cat
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
This boxplot shows us that those who choose to sit in the back tend to drink more alcohol.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Boxplot shows those who drink more alcohol sit in the back.

## Numerical Summarys 

## Inferential Tests

## Conclusions


